---
title: "Homework 03"
author: "Zoe Stopfer"
date: "2026/03/03"
format: html
editor: visual
https://github.com/ZS-25-bit/ENVS-193DS_homework-03.git
---

```{r}
#| label: Reading in Packages
#| message: false
# reading in packages 
library(tidyverse) 
library(here)
library(flextable)
library(janitor)
salinity <- read_csv(here("Data", "salinity-pickleweed.csv")) # reading salinity data 
my_data <- read_csv(here("Data", "JJMood4.csv")) |> # read in JJ Mood and make into a object
  clean_names() # clean column names
```

# Problem 1. Slough Soil Salinity

## a.

Pearson's correlation and Spearman rank correlation are appropriate tests to determine the strength of the relationship between Salinity and California pickleweed biomass because correlation can be used independently of a linear model because the 2 variables are related to each other. Pearson's correlation is a parametric test that would show the linear relationship between slough soil salinity and pickleweed biomass. Spearman rank correlation is a non-parametric test that would show the monotonic relationship between slough soil salinity and pickleweed biomass.

## b.

```{r}
#| label: Creating scatterplot 
ggplot(data = salinity, # use the salintiy data frame
       aes(x = pickleweed, # x-axis
           y = salinity_mS_cm,)) + # y-axis
  geom_point(color = "palegreen3") + # adding points and changin color
  labs(x = "California Picklweed Biomass(g)", # relabelling the x-axis
       y = "Salinity(mS/cm)", # and the y-axis
       title = "As Pickleweed Biomass Growth Increases Slough Salintiy Increases") # adding title
theme_gray() # changing theme 
```

## c.

```{r}
#| label: Spearman plot
ggplot(data = salinity, # use the salintiy data frame
       aes(x = pickleweed, # x-axis
           y = salinity_mS_cm,)) + # y-axis
  geom_point(color = "orchid4") + # adding points and changin color
  labs(x = "California Picklweed Biomass(g)", # relabelling the x-axis
       y = "Salinity(mS/cm)", # and the y-axis
       title = "As Pickleweed Biomass Growth Increases Slough Salintiy Increases") # adding title
theme_gray() # changing theme 
```

```{r}
#| label: spearman test
cor.test(salinity$salinity_mS_cm,salinity$pickleweed, # adding in data frame and columns 
         method = "spearman") # this spearman test 
```

The test I ran was the Spearman rank correlation. The assumptions I checked was if there were 1) independent observations and 2) a monotonic relationship between variables. The independent observations in the problem were the slough soil salinity and the pickleweed biomass. The monotonic relationship can be seen in the scatterplot where the dots are following a consistent direction of a curve going up. Since the data is related to each and it aligns with our assumptions, Spearman rank correlation was a appropriate test.

## d.

To evaluate the strength of the relationship between pickleweed biomass and soil salinity, I used a Spearman rank correlation test. Based off the test, we found a moderate relationship between pickleweed biomass and soil salinity ( Spearman ρ = 0,59, S = 824, p = 0.003, α = 0.05).

## e.

Based of the results of the test, we can conclude that the pickleweed biomass increases when the solute soil salinity increases. The graph shows that the data moves in a upward curve as both mS/cm increases when g increases. If we want to restore the population of pickleweed, we should plant them in soil with higher salinity.

## f.

```{r}
#| label: Pearson's plot
ggplot(data = salinity, # use the salintiy data frame
       aes(x = pickleweed, # x-axis
           y = salinity_mS_cm,)) + # y-axis
  geom_point(color = "aquamarine4") + # adding points and changin color
  labs(x = "California Picklweed Biomass(g)", # relabelling the x-axis
       y = "Salinity(mS/cm)", # and the y-axis
       title = "As Pickleweed Biomass Growth Increases Slough Salintiy Increases") # adding title
theme_gray() # changing theme 
```

```{r}
#| label: testing if normally distributed
ggplot(data = salinity, 
       aes(x = pickleweed)) + # x-axis
  # first layer: histogram
  geom_histogram(bins = 6, # bins from Rice Rule (approximate)
                 fill = "orange",
                 color = "black") + 
  theme_minimal() +
  labs(x = "Calinfornia Picklweed Biomass(g)", # naming x and y axis 
       y = "Salinity(mS/cm)")


```

```{r}
#| label: Pearson's test 
 cor.test(salinity$salinity_mS_cm,salinity$pickleweed, # adding in data frame and columns 
         method = "pearson") # this pearson's test 

```

The two test would have not led us in the same direction. The Pearson's correlation, when testing if its normally distributed shows that the data is not perfect, but this can happen with larger data sets. However the Pearson's correlation test gave us a positive number indicating that there is a positive and "strong" relationship between soil salinity and pickleweed biomass. In the end, both test seem to lean towards there being a positive relationship between both variables.

# Problem 2. Personal data

## a.

```{r}
ggplot(data = my_data, # use my_data frame 
       aes(x = attendance)) + #add x-axis
  geom_histogram(stat = "count", #  creates a histogram 
                 fill = "#FF4500", # fill in bar with color
                 color = "darkorchid3") + # outline bar 
  facet_wrap(~mood_category) + # separated by each mood
  labs(title = "Mood Based on Going/Not Going to Jiu Jitsu", # add title
       x = "Attendance", # label x-axis
       y = "Frequency") + # label y-axis 

  theme_grey()+ # change theme
  theme(legend.position = "none") # remove legend 
```

```{r}
ggplot(data = my_data, # use my_data data frame
       aes(x = dates, # create x-axis and y-axis
           y = mood_category,
           color = mood_category)) + # color mood_category 
  geom_point() + # adding points
  labs( x = "Date", # relabelling x, y, title, and color
        y = "Mood",
        title = "Mood Throughout Time",
        color = "Mood Category") +
  theme_grey() # change theme
```

## b.

**Figure 1. Going/Not Going to Jiu Jitsu:** Columns represent counts of attendance in regards of going or not going to jiu Jitsu. Distributions of attendance are represented in four panels based on my emotion at the end of day in regards to attendance: HEP "high energy positive"(top left), HEU" high energy unpleasant" (top right), LEP "low energy positive" (bottom left), and LEU " low energy unpleasant"(bottom right) .

**Figure 2. Mood Throughout Time.** Each dot represents the mood I felt at the end of the day in regards of my attendance of going to jiu jitsu. It is split up into four mood categories: red is HEP( high energy positive), green is HEP( high energy unpleasant), blue is LEP( low energy positive), and purple is LEU( low energy unpleasant).

# Problem 3. Affective visualization

## a.

## b.

## c.

## d.

## e.

# Problem 4. Statistical critique

## a.

## b.

## c.

## d.
