---
title: "Homework 03"
author: "Zoe Stopfer"
date: "2026/03/03"
format: html
editor: visual
https://github.com/ZS-25-bit/ENVS-193DS_homework-03.git
---

```{r}
#| label: Reading in Packages
#| message: false
# reading in packages 
library(tidyverse) 
library(here)
library(flextable)
library(janitor)
salinity <- read_csv(here("Data", "salinity-pickleweed.csv"))
my_data <- read_csv(here("Data", "JJMood4.csv")) |> # read in JJ Mood and make into a object
  clean_names() # clean column names
```

# Problem 1. Slough Soil Salinity

## a.

## b.

```{r}
#| label: Creating scatterplot 
ggplot(data = salinity, # use the salintiy data frame
       aes(x = pickleweed, # x-axis
           y = salinity_mS_cm,)) + # y-axis
  geom_point(color = "palegreen3") + # adding points and changin color
  labs(x = "California Picklweed Biomass(g)", # relabelling the x-axis
       y = "Salinity(mS/cm)", # and the y-axis
       title = "Pickleweed Growth based on Slough Salintiy") # adding title
theme_gray() # changing theme 
```

## c. 

## d. 

## e. 

## f. 

# Problem 2. Personal data

## a.

```{r}
ggplot(data = my_data, # use my_data frame 
       aes(x = attendance)) + #add x-axis
  geom_histogram(stat = "count", #  creates a histogram 
                 fill = "#FF4500", # fill in bar with color
                 color = "darkorchid3") + # outline bar 
  facet_wrap(~mood_category) + # separated by each mood
  labs(title = "Mood Based on Going/Not Going to Jiu Jitsu", # add title
       x = "Attendance", # label x-axis
       y = "Frequency") + # label y-axis 

  theme_grey()+ # change theme
  theme(legend.position = "none") # remove legend 
```

```{r}
ggplot(data = my_data, # use my_data data frame
       aes(x = dates, # create x-axis and y-axis
           y = mood_category,
           color = mood_category)) + # color mood_category 
  geom_point() + # adding points
  labs( x = "Date", # relabelling x, y, title, and color
        y = "Mood",
        title = "Mood Throughout Time",
        color = "Mood Category") +
  theme_grey() # change theme

```

## b.

**Figure 1. Mood Based on Going/ Not Going to Jiu Jitsu.** Each section represents a different mood category that my day could have fallen on whether or not I attended or did not attend Jiu Jitsu. "HEP" means "High Energy Positive" mood. "HEU" means "Hig Small black points represent measurements of crab carapace widths at three sites: Zeke’s Island National Estuarine Research Reserve (NERR), Virginia Coastal Reserve Long-Term Ecological Research (LTER) site, and Cape Cod. Large red points represent mean crab carapace width. Data originally from: Johnson, D. 2019. Fiddler crab body size in salt marshes from Florida to Massachusetts, USA at PIE and VCR LTER and NOAA NERR sites during summer 2016. ver 1. Environmental Data Initiative.
